---
title: "Effect of Vitamin C on Tooth Growth in Guinea Pigs"
author: "Himank Jain"
date: "March 17, 2019"
output: pdf_document
---

## Overview

* We use 'ToothGrowth' dataset and perform exploratory analysis on it.
* Then we use confidence intervals and hypothesis tests to compare tooth growth.

## Exploratory Analysis:

```{r}
library(datasets)
library(ggplot2)
head(ToothGrowth)
tail(ToothGrowth)
summary(ToothGrowth)
str(ToothGrowth)
```

Plotting boxplot of toothlength per dosages & supplement:

```{r}
data <- ToothGrowth
levels(data$supp) <- c("OrangeJuice", "AscorbicAcid")
g <- ggplot(data, aes(x = factor(dose), y = len))
g <- g + facet_grid(.~supp)
g <- g + geom_boxplot(aes(fill = supp))
g <- g + labs(title = "Tooth Length")
g <- g + labs(x = "Dose (mg/day)", y = "Tooth Length")
print(g)
```

We observe Orange juice shows better results for 0.5 and 1 mg/day dosages however 2 mg/day results are quite similar

## Assumptions

We assume from here, ToothGrowth data follows normal distribution.

## Hypothesis Tests

* Testing three different hypothesis  

1) For x = 0.5 mg/day

```{r}
h0.5 <- t.test(len ~ supp, data = subset(data, dose == 0.5))
h0.5$conf.int
h0.5$p.value
```

We reject null hypothesis as the p-value is smaller than significant level of 0.05.
Therefore orange juice results in more tooth growth than absorbic acid.


2) For x = 1 mg/day

```{r}
h1 <- t.test(len ~ supp, data = subset(data, dose == 1))
h1$conf.int
h1$p.value
```

We again reject null hypothesis as the p-value is smaller than significant level of 0.05.
Therefore orange juice results in more tooth growth than absorbic acid.

3) For x = 2 mg/day

```{r}
h2 <- t.test(len ~ supp, data = subset(data, dose == 2))
h2$conf.int
h2$p.value
```

Now, p-value is larger than the significance level of 0.05. therefore we cannot reject null hypothesis. Therefor orange juice and absorbic acid have same effect now.

## Conclusions

We conducted three hypothesis tests. We inferred that Orange juice is better for tooth growth in guinea pigs in doses of 0.5 and 1 mg/day. however no difference between orange juice and absorbic acid for 2 mg/day dosage. 
